List of published trait datasets and databases

### 2018-10-19 manuscript/appendix_A.Rmd
adjust appendix_A.Rmd to new template and author list

---
title: "Towards an Ecological Trait-data Standard - Appendix A"
author:
- name: Florian D. Schneider \footnotemark[1] \footnotemark[2] \footnotemark[3]
- name: Malte Jochum \footnotemark[4]
- name: Gaëtane Le Provost \footnotemark[3]
- name: Andreas Ostrowski \footnotemark[6]
- name: Caterina Penone \footnotemark[4]
- name: David Fichtmüller \footnotemark[5]
- name: Martin M. Gossner \footnotemark[8]
- name: Anton Güntsch \footnotemark[5]
- name: Birgitta König-Ries\footnotemark[6]
- name: Pete Manning \footnotemark[3]
- name: Nadja K. Simons \footnotemark[7]
fontsize: 12pt
geometry: margin=0.5in
classoption: landscape
output:
  pdf_document:
    fig_caption: yes
    fig_crop: no
    keep_tex: yes
    template: pretty.template
  html_document:
    fig_caption: yes
    fig_width: 4
    highlight: null
    keep_md: yes
    theme: united
  word_document:
    fig_caption: yes
    fig_width: 6
---

@@

\footnotetext[1]{Corresponding author: florian.dirk.schneider@gmail.com}
\footnotetext[2]{Institute of Linguistics and Literary Studies, Technische Universität Darmstadt, Darmstadt, Germany}
\footnotetext[3]{Senckenberg Biodiversity and Climate Research Centre (BiK-F) Frankfurt am Main, Germany}
\footnotetext[4]{Institute of Plant Sciences, University of Bern, Bern, Switzerland}
\footnotetext[5]{Botanic Garden and Botanical Museum Berlin, Freie Universität Berlin, Berlin, Germany}
\footnotetext[6]{Department of Mathematics and Computer Science, Friedrich-Schiller-Universität Jena, Jena, Germany}
\footnotetext[8]{Forest Entomology, Swiss Federal Research Institute WSL, Birmensdorf, Switzerland} <!--  Zürcherstrasse 111, CH-8903 -->
\footnotetext[7]{Department of Ecology and Ecosystem Management, Technische Universität München, Freising, Germany}

@@

```{r, echo = FALSE, warning = FALSE}
options(knitr.table.format = "latex")
library(kableExtra)
gg <- read.csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTfQOIHjJv5x_YHgq14DR7VLTvycfsl2Njj2Ip4p2a5kca8AX5t5cmaial6Bg-MX9pBDOJaJfnlR7Qj/pub?output=csv", encoding = "UTF-8")
dt <- subset(gg, select = c(datasetName, type, DOI, organismFocus, regionalFocus, NumberTaxa, NumberTraits, Responsible, CiteAs, TermsOfUse))

@@

order <- c(14, 15,30,  # all organisms
           1,4,5,13,18,20,21, # plants
           11,16,25,33, # all animals
           3,17,31, ## birds
           7,34,12, # mammals
           26,8,27, # other vertebrates
           32,2, 6,9,23,10,22,29,# invertebrates
           24,28, # fungi
           19 # other
           )

>>>>

---
title: "List of published trait datasets and databases"
subtitle: "Towards an Ecological Trait-data Standard - Supplementary Material A"
author:
- name: Florian D. Schneider \footnotemark[1]  \footnotemark[2]
- name: David Fichtmüller \footnotemark[5]
- name: Martin M. Gossner \footnotemark[8]
- name: Anton Güntsch \footnotemark[5]
- name: Malte Jochum \footnotemark[4]
- name: Birgitta König-Ries\footnotemark[6]
- name: Gaëtane Le Provost \footnotemark[2]
- name: Pete Manning \footnotemark[2]
- name: Andreas Ostrowski \footnotemark[6]
- name: Caterina Penone \footnotemark[4]
- name: Nadja K. Simons \footnotemark[7]
fontsize: 12pt
geometry: margin=0.5in
documentclass: scrartcl
classoption: landscape
output:
  pdf_document:
    fig_caption: yes
    fig_crop: no
    keep_tex: yes
    template: pretty.template
  html_document:
    fig_caption: yes
    fig_width: 4
    highlight: null
    keep_md: yes
    theme: united
  word_document:
    fig_caption: yes
    fig_width: 6
---

@@

\footnotetext[1]{Corresponding author: florian.dirk.schneider@gmail.com}
\footnotetext[2]{Senckenberg Biodiversity and Climate Research Centre (BiK-F) Frankfurt am Main, Germany}
\footnotetext[5]{Botanic Garden and Botanical Museum Berlin, Freie Universität Berlin, Berlin, Germany}
\footnotetext[8]{Forest Entomology, Swiss Federal Research Institute WSL, Birmensdorf, Switzerland} <!--  Zürcherstrasse 111, CH-8903 -->
\footnotetext[4]{Institute of Plant Sciences, University of Bern, Bern, Switzerland}
\footnotetext[6]{Department of Mathematics and Computer Science, Friedrich-Schiller-Universität Jena, Jena, Germany}
\footnotetext[7]{Department of Ecology and Ecosystem Management, Technische Universität München, Freising, Germany}

@@

```{r, echo = FALSE, warning = FALSE}
options(knitr.table.format = "latex")
library(kableExtra)

gg <- read.csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTfQOIHjJv5x_YHgq14DR7VLTvycfsl2Njj2Ip4p2a5kca8AX5t5cmaial6Bg-MX9pBDOJaJfnlR7Qj/pub?output=csv", encoding = "UTF-8")
dt <- subset(gg, select = c(datasetName, type, DOI, organismFocus, regionalFocus, NumberTaxa, NumberTraits, Responsible, CiteAs, TermsOfUse))

@@

order <- c(14, 15,  # all organisms
           1,4,5,13,18,20,21, # plants
           11,16,25,30,33, # all animals
           3,17,31, ## birds
           7,34,12, # mammals
           26,8,27, # other vertebrates
           32,2, 6,9,23,10,22,29,19, # invertebrates
           24,28 # fungi
           # other
           )
